Classless Java

### 2015-11-13 paper/sections/Introduction.tex
Some revision on the Introduction

To formalize object interfaces, we propose Featherweight Object Interfaces (FOI): 
a FeatherweightJava-style calculus, which captures the essence 
of interfaces with default methods. The semantics of object interfaces 
is given as a type-directed translation from FOI to itself. 
In the resulting FOI code all object interfaces are translated into 
regular FOI (and Java) interfaces with default methods. The translation 
is proved to be type-preserving, ensuring that the translation does 
not introduce type-errors. One interesting aspect of the theorem is that, 
if we ignore the object annotations, the program still type-checks 
under the regular typing rules of FOI (and Java).\bruno{double-check!}

@@

\item {\bf Object interfaces:} A simple language feature that allows 
various powerful programming idioms to be expressed conveniently in
Java. Object interfaces are pure sugar: they can be desugared into standard Java 
code, without loss of modularity or type-safety.

\item {\bf Featherweight Object (FC):} A simple formal calculus that models 
the essential features of Java 8 interfaces with default methods, and 
can be used to formally define the desugaring of object interfaces. 
We prove ...

@@

\bruno{Useful reference, perhaps, on the discussion of why not override object 
methods: 
\url{http://mail.openjdk.java.net/pipermail/lambda-dev/2013-March/008435.html}}

>>>>

To formalize object interfaces, we propose Featherweight Object
Interfaces (FOI)\bruno{should we just call it Featherweight Classless
  Java?}: 
a FeatherweightJava-style calculus, which captures the essence 
of interfaces with default methods. The semantics of object interfaces 
is given as a type-directed translation from FOI to itself. 
In the resulting FOI code all object interfaces are translated into 
regular FOI (and Java) interfaces with default methods. The translation 
is proved to be type-preserving, ensuring that the translation does 
not introduce type-errors. One interesting aspect of the theorem is that, 
if we ignore the object annotations, the program still type-checks 
under the regular typing rules of FOI (and Java).\bruno{double-check!}

FOI's usefulness goes beyond serving as a calculus to formalize object
interfaces. During the development process of FOI, we encountered an 
incoherent behaviour in Java's implementation of default methods that 
could be classified as a bug. \bruno{Should we report bug to the Java
  developers mailing list?}

@@

\item {\bf Object Interfaces:} A simple language feature that allows 
various powerful programming idioms to be expressed conveniently in
Java. Object interfaces are pure sugar: they can be desugared into standard Java 
code, without loss of modularity or type-safety.

\item {\bf Featherweight Object Interfaces (FOI):} A simple formal calculus that models 
the essential features of Java 8 interfaces with default methods, and 
can be used to formally define the desugaring of object interfaces. 
We prove ...

\item {\bf A Bug in the Implementation of Java 8:}\bruno{state this as
  a contrib?}

@@

\bruno{Useful reference, perhaps, on the discussion of why not override object 
methods: 
\url{http://mail.openjdk.java.net/pipermail/lambda-dev/2013-March/008435.html}}
\bruno{Maybe Marco's text can be in the conclusion, which I think is
  ok to be more provocative. I tried to be a bit more contained in the
Introduction.}
